Wikipedia Text Mining and Surprisal Analysis

### 2019-07-16 surprisal/WALS_features.Rmd
not enough memory to run models for all of the features

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in data}
wals <- read_csv(here("Data/wals.csv"))
feature_names <- read_feather(here("Wikipedia/feature_names.feather"))

@@

```{r see which WALS features are the most complete for our languages}
all_languages <- wals %>% 
  filter(language %in% LANGUAGES) %>% 
  filter(rowSums(is.na(.)) < 130) %>%
  group_by(language) %>%
  slice(1) %>%
  ungroup() 
```

@@

```{r comparison: features to cosines}
imputed_df <- common_df %>% 
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  sapply(as.factor) %>%
  as.data.frame() %>%
  column_to_rownames("language") %>% 
  MIMCA(ncp = 1)

imputed_df <- as.data.frame(imputed_df[[1]][[99]])

wo_sub <- imputed_df %>% 
  rownames_to_column("language") %>%
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = as.numeric(as.factor(value)))

cosines <- wkpd %>%
  filter(language %in% common_languages) %>%
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, cosine, -language1)

wf_pairwise <- expand.grid(language1 = wo_sub$language,
                           language2 = wo_sub$language) %>%
  left_join(wo_sub, by = c("language1" = "language")) %>%
  rename(value1 = value) %>%
  left_join(wo_sub, by = c("language2" = "language", "feature")) %>%
  rename(value2 = value) %>%
  mutate(same = value1 == value2) %>%
  select(-value1, -value2) %>%
  left_join(cosines, by = c("language1", "language2"))

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(lingtypology)
library(feather)
library(here)
library(missMDA)
library(lsa)
knitr::opts_chunk$set(echo = TRUE)
```

```{r read in data}
wals <- read_csv(here("Data/wals_isos.csv"))
feature_names <- read_feather(here("Wikipedia/feature_names.feather"))

@@

```{r see which WALS features are the most complete for our languages}
all_languages <- wals %>% 
  filter(rowSums(is.na(.)) < 130) %>%
  group_by(language) %>%
  slice(1) %>%
  ungroup() 
```

@@

```{r models}
imputed_df <- read_csv(here("Data/imputed_wals.csv"))

wf_sub <- imputed_df %>% 
  group_by(language) %>%
  slice(1) %>%
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = as.numeric(as.factor(value)))

cosines <- wiki %>%
  filter(language %in% common_languages, gram == "Unigram") %>%
  select(-gram) %>% 
  column_to_rownames("language") %>%
  t() %>%
  cosine() %>%
  as_data_frame(rownames = "language1") %>%
  gather(language2, cosine, -language1)

wf_pairwise <- expand.grid(language1 = wf_sub$language,
                           language2 = wf_sub$language) %>%
  left_join(wf_sub, by = c("language1" = "language")) %>%
  rename(value1 = value) %>%
  left_join(wf_sub, by = c("language2" = "language", "feature")) %>%
  rename(value2 = value) %>%
  mutate(same = value1 == value2) %>%
  select(-value1, -value2) %>%
  left_join(cosines, by = c("language1", "language2"))

@@

```{r imputation}
imputed_df <- common_df %>% 
  gather(feature, value, -language) %>%
  group_by(feature) %>%
  mutate(value = factor(value)) %>%
  select(language, feature, value) %>%
  ungroup() %>% 
  spread(feature, value) %>% 
  sapply(as.factor) %>%
  as.data.frame() %>%
  column_to_rownames("language") %>% 
  MIMCA(ncp = 1)

imputed_df <- as.data.frame(imputed_df[[1]][[99]]) 
```

### 2019-07-16 surprisal/wiki_surprisal.Rmd
not enough memory to run models for all of the features

wals_isos <- wals %>%
  mutate(iso = iso.gltc(glottocode)) %>%
  select(-glottocode)

wals_isos %>% 
  inner_join(codes, by = "iso") %>% 
  select(-language.x) %>%
  rename(language = language.y) %>% 
  inner_join(wiki %>% inner_join(codes, by = "language"), by = "iso")
```

>>>>

wals %>%
  mutate(iso = iso.gltc(glottocode)) %>%
  select(-glottocode) %>% 
  inner_join(codes, by = "iso") %>% 
  select(-language.x) %>%
  rename(language = language.y) %>%
  write_csv(here("Data/wals_isos.csv"))

#  inner_join(wiki %>% inner_join(codes, by = "language"), by = "iso")
```
